---
name: Wenbo Lv
position: "undergraduate"
github: SpatLyu
www: spatlyu.github.io
orcid: 0009-0002-6003-3800
email: "lyu.geosocial@gmail.com"
address: "Xi'an, Shaanxi"
# date: "`r Sys.Date()`"
output: vitae::hyndman
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

# Some stuff about me

-   I am deeply interested in developing new spatial analysis methods based on spatial relationships (such as spatial dependence, spatial heterogeneity, geographical similarity) to support urban sustainability and climate change mitigation.
-   I am proficient in R language data analysis, statistical modeling, and R package development.
-   I am familiar with implementing computationally complex statistical algorithms using C++, and I can flexibly call upon torch.

# Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Geographic Information Science", "2021-2025", "Shaanxi Normal University", "Xi'an, Shaanxi",
) %>%
  detailed_entries(Degree, Year, Institution, Where)
```

# Honor

```{r}
tribble(
  ~ Awards, ~ Date,
  "Grand Prize in the 12th National University Student GIS Application Skills Competition", "2023.12",
  "First Prize in the Second National University Student Ecological Environment Management Research Innovation Competition", "2023.11",
  "Second Prize of the 5th 'Guodi Cup' National College Student Natural Resource Science and Technology Competition, China Society of Natural Resources", "2023.12",
  "Outstanding Individual in Military Training Publicity for College Students, Shaanxi Normal University", "2021.10",
  "National University Student Innovation and Entrepreneurship Training Program Qualified Completion", "2024.06"
) %>%
  detailed_entries(Awards,Date)
```

# Developed Spatial Analysis Toolkit

| Package       | Description                                                   | Source Code                                | Language       |
|---------------|---------------------------------------------------------------|--------------------------------------------|----------------|
| gdverse       | Family of geographical detector models in R                   | <https://github.com/ausgis/gdverse>        | R, C++, Python |
| geocomplexity | Mitigate Spatial Bias through Geographical Complexity         | <https://github.com/ausgis/geocomplexity>  | C++, Python, C |
| geosimilarity | Geographically Optimal Similarity                             | <https://ausgis.github.io/geosimilarity/>  | R              |
| spEcula       | Spatial Prediction Methods In R                               | <https://github.com/SpatLyu/spEcula>       | R              |
| tidyrgeoda    | A tidy interface for rgeoda                                   | <https://github.com/SpatLyu/tidyrgeoda>    | R              |
| SpatBox       | A Python Library For GeoSpatial Data Propressing and Modeling | <https://github.com/SpatLyu/spatbox>       | Python         |
| qgisprocess   | R package to use QGIS processing algorithms                   | <https://r-spatial.github.io/qgisprocess/> | R              |
| Rsagacmd      | A package for linking R with the open-source SAGA-GIS         | <https://stevenpawley.github.io/Rsagacmd/> | R              |
| sdsfun        | Functions for Spatial Data Science                            | <https://github.com/SpatLyu/sdsfun>        | R              |
| geocn         | Loads Spatial Data Sets of China                              | <https://github.com/SpatLyu/geocn>         | R              |

# In research

```{r}
tribble(
  ~ Name, ~ Role, ~ Date, ~ Details,
  "Extraction of Urban Spatial Boundaries in Xi'an City Using Deep Learning", "Leader", "",
  "Combining advanced spatial sampling and unsupervised algorithms to automatically construct sample sets, and then using geographical neural networks weighted logistic regression to extract urban spatial boundaries",
  "Geocomplexity mitigates spatial bias", "Leader", "",
  "Considering the Complexity of Spatial Data in Spatial Data Analysis to Improve Modeling Accuracy"
) %>%
  detailed_entries(Name, Role, ,Date ,Details)
```

# Unpublished

```{r}
tribble(
  ~ Name, ~ Role, ~ Status,
    "Distinguishing the impacts and gradient effects of climate change and human activities on vegetation cover in the Weihe River Basin , China", "First Author", "Under revision",
  "gdverse : An R package for spatial stratified heterogeneity modeling through geographical detectors", "First Author", "In writing"
) %>%
  detailed_entries(Name, Role, Status)
```

# Publications

```{r}
bibliography_entries("lyu.bib")
```
