---
name: Wenbo Lv
position: "undergraduate"
github: SpatLyu
www: spatlyu.github.io
orcid: 0009-0002-6003-3800
email: "lyu.geosocial@gmail.com"
address: "Xi'an, Shaanxi"
# date: "`r Sys.Date()`"
output: vitae::hyndman
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

# Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Geographic Information Science", "2021-2025", "Shaanxi Normal University", "Xi'an, Shaanxi",
) %>%
  detailed_entries(Degree, Year, Institution, Where)
```

# Some stuff about me

- I am passionate about **developing innovative spatial analysis methods** that **leverage spatial relationships**, such as *spatial dependence*, *spatial heterogeneity*, and *geographical similarity*, to advance *urban sustainability* and *climate change mitigation* efforts.
- I am proficient in *data analysis*, *statistical modeling*, and developing *R packages*, as well as open-source analytical software using **R**, **C++**, and **Python**.
- I have experience implementing complex statistical algorithms in **C++** and can efficiently integrate **torch** for machine learning applications.

# Publications

```{r}
bibliography_entries("lyu.bib")
```

# Honor

```{r}
tribble(
  ~ Awards, ~ Date,
  "Grand Prize in the 12th National University Student GIS Application Skills Competition", "2023.12",
  "First Prize in the Second National University Student Ecological Environment Management Research Innovation Competition", "2023.11",
  "Second Prize of the 5th 'Guodi Cup' National College Student Natural Resource Science and Technology Competition, China Society of Natural Resources", "2023.12",
  "Outstanding Individual in Military Training Publicity for College Students, Shaanxi Normal University", "2021.10",
  "National University Student Innovation and Entrepreneurship Training Program Qualified Completion", "2024.06"
) %>%
  detailed_entries(Awards,Date)
```

# In research

```{r}
tribble(
  ~ Name, ~ Role, ~ Date, ~ Details,
  "Extraction of Urban Spatial Boundaries in Xi'an City Using Deep Learning", "Leader", "",
  "Combining advanced spatial sampling and unsupervised algorithms to automatically construct sample sets, and then using geographical neural networks weighted logistic regression to extract urban spatial boundaries",
  "Geocomplexity mitigates spatial bias", "Leader", "",
  "Considering the Complexity of Spatial Data in Spatial Data Analysis to Improve Modeling Accuracy"
) %>%
  detailed_entries(Name, Role, ,Date ,Details)
```

# Unpublished

```{r}
tribble(
  ~ Name, ~ Role, ~ Status,
  "gdverse: An R package facilitating spatial stratified heterogeneity analysis with geographical detectors", "First Author", "In writing",
  "Generalized Geographical Detector", "First Author", "In writing"
) %>%
  detailed_entries(Name, Role, Status)
```

# Developed Spatial Analysis Toolkit

| Package       | Description                                                   | Source Code                                | Language       |
|---------------|---------------------------------------------------------------|--------------------------------------------|----------------|
| geocomplexity | Mitigate Spatial Bias Through Geographical Complexity         | <https://github.com/ausgis/geocomplexity>  | C++, R, C |
| geosimilarity | Geographically Optimal Similarity                             | <https://github.com/ausgis/geosimilarity>  | R              |
| esp           | Enhanced Stratified Power                                      | <https://github.com/ausgis/esp>            | R, C++         |
| sdsfun        | Spatial Data Science Complementary Features                   | <https://github.com/stscl/sdsfun>          | R, C++         |
| gdverse       | Analysis of Spatial Stratified Heterogeneity                  | <https://github.com/stscl/gdverse>         | R, C++, Python |
| geocn         | Loads Spatial Data Sets of China                              | <https://github.com/stscl/geocn>           | R              |
| spEcula       | Spatial Prediction Methods In R                               | <https://github.com/SpatLyu/spEcula>       | R              |
| tidyrgeoda    | A tidy interface for rgeoda                                   | <https://github.com/SpatLyu/tidyrgeoda>    | R              |
| SpatBox       | A Python Library For GeoSpatial Data Propressing and Modeling | <https://github.com/SpatLyu/spatbox>       | Python         |
| qgisprocess   | R package to use QGIS processing algorithms                   | <https://github.com/r-spatial/qgisprocess> | R              |
| Rsagacmd      | A package for linking R with the open-source SAGA-GIS         | <https://github.com/stevenpawley/Rsagacmd> | R              |