---
name: Wenbo Lv
position: "undergraduate"
github: SpatLyu
www: spatlyu.github.io
orcid: 0009-0002-6003-3800
email: "lyu.geosocial@gmail.com"
address: "Xi'an, Shaanxi"
# date: "`r Sys.Date()`"
output: vitae::moderncv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

# Some stuff about me

- I am passionate about **developing innovative spatial analysis methods** that leverage **spatial relationships**, such as *spatial dependence*, *spatial heterogeneity*, and *geographical similarity*, to advance *urban sustainability* and *climate change mitigation* efforts.
- I possess expertise in *data analysis*, *statistical modeling*, and the development of *R packages* and open-source analytical tools utilizing **R**, **C++**, and **Python**.
- I have contributed to the **development** and **maintenance** of several open-source spatial analysis tools within the R community and remain dedicated to **advancing open-source geospatial analysis software**.

# Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "BSc In Geographic Information Science", "2021-2025", "Shaanxi Normal University", "Xi'an, Shaanxi",
) %>%
  detailed_entries(Degree, Year, Institution, Where)
```

# Publications

```{r}
bibliography_entries("../lyu_publications.bib")
```

# Honor

```{r}
tribble(
  ~ Awards, ~ Date,
  "Grand Prize in the 12th National University Student GIS Application Skills Competition", "2023.12",
  "First Prize in the Second National University Student Ecological Environment Management Research Innovation Competition", "2023.11",
  "Second Prize of the 5th 'Guodi Cup' National College Student Natural Resource Science and Technology Competition, China Society of Natural Resources", "2023.12",
  "Outstanding Individual in Military Training Publicity for College Students, Shaanxi Normal University", "2021.10",
  "National University Student Innovation and Entrepreneurship Training Program Qualified Completion", "2024.06"
) %>%
  detailed_entries(Awards,Date)
```

# Unpublished

```{r}
tribble(
  ~ Name, ~ Role, ~ Status,
  "gdverse: An R package for spatial stratified heterogeneity family", "First Author", "Submitting to TGIS",
  "On the role of explicit spatial information in stratified heterogeneity", "First Author", "Writing in progress, planning to submit to AAAG",
  "A correlation indicator based on spatial patterns", "First Author", "Writing in progress, planning to submit to IJGIS",
  "Geocomplexity Mitigates Spatial Bias", "First Author", "Writing in progress, planning to submit to IJGIS"
) %>%
  detailed_entries(Name, Role, Status)
```

# In research

```{r}
tribble(
  ~ Name, ~ Role, ~ Date, ~ Details,
  "Extract Urban Spatial Boundaries in Xi'an City Using Deep Learning", "Leader", "",
  "Utilized advanced spatial sampling methods and unsupervised algorithms to automatically generate sample sets. Employed geographically weighted neural networks combined with logistic regression to extract urban spatial boundaries"
) %>%
  detailed_entries(Name, Role, Date, Details)
```

# Developed Spatial Analysis Toolkit

- **[gdverse](https://github.com/stscl/gdverse)**  
  Provides tools for analyzing *Spatial Stratified Heterogeneity* (SSH), integrating advanced statistical methods to assess spatial patterns effectively. Developed using **R**, **C++**, and **Python**.  

- **[sesp](https://github.com/stscl/sesp)**  
  Implements the *Spatially Explicit Stratified Power* model, a robust framework for spatial analysis combining stratification and statistical power. Written in **R** and **C++**.  

- **[geocomplexity](https://github.com/ausgis/geocomplexity)**  
  Focuses on mitigating spatial biases by leveraging geographical complexity. Combines computational efficiency with flexibility, developed in **C++**, **R**, and **C**.  

- **[cisp](https://github.com/stscl/cisp)**  
  Introduces a novel *Correlation Indicator Based on Spatial Patterns* for measuring spatial correlations with high precision. Written in **R**.  

- **[geosimilarity](https://github.com/ausgis/geosimilarity)**  
  Provides methods for calculating *Geographically Optimal Similarity*, enabling better spatial predict. Developed in **R**.  

- **[GD](https://github.com/ausgis/GD)**  
  Implements *Geographical Detectors*, a toolkit for assessing spatial factors influencing heterogeneity. Fully developed in **R**.  

- **[sdsfun](https://github.com/stscl/sdsfun)**  
  Adds complementary features for *Spatial Data Science*, providing user-friendly functionalities for geospatial research. Developed using **R** and **C++**.  

- **[geocn](https://github.com/stscl/geocn)**  
  Simplifies the process of loading and managing spatial datasets of China, supporting research with localized datasets. Developed in **R**.  

- **[qgisprocess](https://github.com/r-spatial/qgisprocess)**  
  Offers an **R** interface to *QGIS processing algorithms*, enabling seamless integration of QGIS functionalities into R workflows.  

- **[spEcula](https://github.com/SpatLyu/spEcula)**  
  Provides advanced methods for *Spatial Prediction* in **R**, supporting applications ranging from environmental modeling to spatial econometrics.  

- **[tidyrgeoda](https://github.com/SpatLyu/tidyrgeoda)**  
  Offers a tidy interface for *rgeoda*, bridging geospatial analysis and tidyverse workflows to streamline data handling and modeling in **R**.  