---
name: Wenbo Lyu
position: "B.Sc. Graduate"
email: "lyu.geosocial@gmail.com"
scholar: NnaUl34AAAAJ
orcid: 0009-0002-6003-3800
#address: "Hong Kong"
#www: spatlyu.github.io
#phone: "+852 56212551"
linkedin: wenbo-lyu-824851403
github: SpatLyu
date: today
date-format: "MMMM YYYY"
headcolor: "000088"
format: hyndmancv-pdf
---

```{r}
#| label: setup
#| include: false

knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  cache = FALSE
)

# Function to produce very basic table, no lines or headings
baretable = \(
  tbl,
  digits = 0,
  include.colnames = FALSE,
  include.rownames = FALSE,
  hline.after = NULL,
  size = getOption("xtable.size", NULL),
  add.to.row = getOption("xtable.add.to.row", NULL),
  longtable = FALSE,
  ...
) {
  xtable::xtable(tbl, digits = digits, ...) |>
    print(
      include.colnames = include.colnames,
      include.rownames = include.rownames,
      hline.after = hline.after,
      comment = FALSE,
      tabular.environment = dplyr::if_else(longtable, "longtable", "tabular"),
      floating = FALSE,
      size = size,
      add.to.row = add.to.row,
      sanitize.text.function = function(x) {
        x
      }
    )
}
```

# Education and qualifications

```{r}
#| label: degrees
#| output: "asis"

tibble::tribble(
  ~Degree, ~Institution, ~Year ,
  "B.Sc. In Geographic Information Science", "Shaanxi Normal University",  "2025",
) |>
  baretable()
```

# Research Experience <!-- Employment history -->

```{r}
#| label: experience
#| output: "asis"

tibble::tribble(
  ~Duration, ~Position,
  "2026.6- ", "Research Assistant, The Hong Kong Polytechnic University", 
  "2025.9-2026.6", "Research Assistant, Eastern Institute of Technology, Ningbo",
  "2024.8-2025.8", "Research Intern, The Hong Kong University of Science and Technology (Guangzhou)", 
) |>
  baretable()
```

# Research interests

- My research interests lie in **advancing methodologies in spatial causal inference** and **developing high-performance computational tools**, with a primary focus on *R packages*.
- Currently, my work centers on **Empirical Dynamic Modeling (EDM)** framework for modeling *dynamic system*, **information theory** for quantifying *information flow* and *variable interactions*, **ordinary differential equations (ODEs)** for characterizing *spatiotemporal processes* and *system evolution*, as well as **counterfactual** and **potential outcomes** framework for estimating *causal effects*. I am particularly interested in leveraging these approaches to address critical challenges in *urban sustainability*, *climate change mitigation*, and broader global issues.
- I specialize in *data analysis*, *statistical modeling*, and developing open-source analytical tools, including *R packages*, using **R**, **C++**, and **Python**, with a strong focus on *spatial analysis*. I actively contribute to the R geospatial community and am dedicated to advancing open-source geospatial software.

# Selected research papers

```{r}
#| label: research-papers
#| output: asis

#papers = RefManageR::ReadBib("./lyu_publications.bib") 
bibtex::read.bib('./lyu_publications.bib')
```

\vspace{0.1cm}

*Note: Publications under "Lyu, W." and "Lv, W." both refer to Wenbo Lyu.*
