---
name: Wenbo Lyu
position: "B.Sc. Graduate"
email: "lyu.geosocial@gmail.com"
scholar: NnaUl34AAAAJ
orcid: 0009-0002-6003-3800
#address: "Hong Kong"
#www: spatlyu.github.io
#phone: "+852 56212551"
linkedin: wenbo-lyu-824851403
github: SpatLyu
date: today
date-format: "MMMM YYYY"
headcolor: "000088"
format: hyndmancv-pdf
---

```{r}
#| label: setup
#| include: false

knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  cache = FALSE
)

# Function to produce very basic table, no lines or headings
baretable = \(
  tbl,
  digits = 0,
  include.colnames = FALSE,
  include.rownames = FALSE,
  hline.after = NULL,
  size = getOption("xtable.size", NULL),
  add.to.row = getOption("xtable.add.to.row", NULL),
  longtable = FALSE,
  ...
) {
  xtable::xtable(tbl, digits = digits, ...) |>
    print(
      include.colnames = include.colnames,
      include.rownames = include.rownames,
      hline.after = hline.after,
      comment = FALSE,
      tabular.environment = dplyr::if_else(longtable, "longtable", "tabular"),
      floating = FALSE,
      size = size,
      add.to.row = add.to.row,
      sanitize.text.function = function(x) {
        x
      }
    )
}
```

# Education and qualifications

```{r}
#| label: degrees
#| output: "asis"

tibble::tribble(
  ~Degree, ~Institution, ~Year ,
  "B.Sc. In Geographic Information Science", "Shaanxi Normal University",  2025,
) |>
  baretable()
```

# Employment history

The `brief` style is a single line per entry: the years at the left, and the
role beside them. `what` is set in bold, and `with` follows it in plain text.

::: {.entries style="brief" fields="{what: Position, with: Organisation, when: Years}"}
| Years     | Position                                     | Organisation                                                        |
|-----------|----------------------------------------------|---------------------------------------------------------------------|
| 2026--    | Vice-Chancellor's Distinguished Professor    | Department of Econometrics & Business Statistics, Monash University |
| 2003--2026| Professor                                    | Department of Econometrics & Business Statistics, Monash University |
| 2016      | KNAW Visiting Professor                      | TU/Eindhoven, Netherlands                                           |
| 2001--2003| Associate Professor                          | Department of Econometrics & Business Statistics, Monash University |
| 1998--2000| Senior Lecturer                              | Department of Econometrics & Business Statistics, Monash University |
| 1995--1996| Lecturer                                     | Department of Mathematics and Statistics, Monash University         |
| 1993--1994| Lecturer                                     | Department of Statistics, University of Melbourne                   |
:::

# Academic and research leadership

A grid table can hold a bullet list in a cell, so `why` carries several points
per entry. The `detailed` style sets those as a bulleted elaboration under the
entry. Here the headings already match, and no `fields` is needed.

::: {.entries style="detailed"}
+-------------+--------------------------+---------------------------------+
| when        | what                     | why                             |
+=============+==========================+=================================+
| 2019--2022  | Head                     | - Department of Econometrics &  |
|             |                          |   Business Statistics, Monash   |
|             |                          | - Led a department of over 70   |
|             |                          |   academic staff                |
+-------------+--------------------------+---------------------------------+
| 2001--2017  | Director                 | - Business & Economic           |
|             |                          |   Forecasting Unit, Monash      |
+-------------+--------------------------+---------------------------------+
:::

# Editorial boards

Markdown inside cells is preserved, and LaTeX special characters are escaped
for you, so *emphasis* and a literal 100% both come out right. `what` is
already set in bold by the style, so `*emphasis*` reads more clearly than
`**bold**` would.

::: {.entries style="brief"}
| when            | what                     | with                                            |
|-----------------|--------------------------|-------------------------------------------------|
| 2023--2026      | Executive Editor         | *The R Journal*                                 |
| 2011--2024      | Editor                   | *Journal of Statistical Software*               |
| 2005--2018      | Editor-in-Chief          | *International Journal of Forecasting*          |
| 2001--2004, 2019-- | Associate Editor      | *International Journal of Forecasting*          |
| 1996--2001      | Book Review Editor       | *Australian Journal of Statistics*              |
:::

# Selected awards and honours

::: {.entries style="brief" fields="{what: Award, with: Awarded by, when: Year}"}
| Year | Award             | Awarded by                     |
|------|-------------------|--------------------------------|
| 2021 | Pitman Medal      | Statistical Society of Australia |
| 2021 | Fellow            | International Institute of Forecasters |
| 2021 | Fellow            | Australian Academy of Science  |
| 2020 | Fellow            | Academy of the Social Sciences in Australia |
| 2007 | Moran Medal for Statistical Science | Australian Academy of Science |
:::

# Research interests

The `skills` style pairs a category with its members, written either as one
string in `with` or as a list in `why`.

::: {.entries style="skills"}
+---------------+----------------------------------------+
| what          | why                                    |
+===============+========================================+
| Methods       | - Forecast reconciliation              |
|               | - Functional time series               |
|               | - Anomaly detection                    |
|               | - Time series visualisation            |
+---------------+----------------------------------------+
| Applications  | - Electricity demand                   |
|               | - Demography                           |
|               | - Tourism                              |
+---------------+----------------------------------------+
| Software      | - R, Rcpp, Stan                        |
+---------------+----------------------------------------+
:::

# Grants

Where the data already lives in a data frame, the same options are given as
cell options instead, and the cell prints a table for the filter to pick up.
See the README for that form.

::: {.entries style="detailed"}
+-------------+----------------------------------------------+---------------------------------------+
| when        | what                                         | why                                   |
+=============+==============================================+=======================================+
| 2019--2024  | Australian Research Council Discovery Grant  | - *Forecasting large collections of   |
|             |                                              |   related time series*                |
|             |                                              | - \$540,000                           |
+-------------+----------------------------------------------+---------------------------------------+
| 2015--2018  | Australian Research Council Linkage Grant    | - *Forecasting electricity demand at  |
|             |                                              |   the household level*                |
|             |                                              | - \$320,000                           |
+-------------+----------------------------------------------+---------------------------------------+
:::
