---
name: Wenbo Lyu
position: "B.Sc. Graduate"
email: "lyu.geosocial@gmail.com"
scholar: NnaUl34AAAAJ
orcid: 0009-0002-6003-3800
#address: "Hong Kong"
#www: spatlyu.github.io
#phone: "+852 56212551"
linkedin: wenbo-lyu-824851403
github: SpatLyu
date: today
date-format: "MMMM YYYY"
headcolor: "000088"
format: hyndmancv-pdf
---

```{r}
#| label: setup
#| include: false

knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  cache = FALSE
)

# Function to produce very basic table, no lines or headings
baretable = \(
  tbl,
  digits = 0,
  include.colnames = FALSE,
  include.rownames = FALSE,
  hline.after = NULL,
  size = getOption("xtable.size", NULL),
  add.to.row = getOption("xtable.add.to.row", NULL),
  longtable = FALSE,
  ...
) {
  xtable::xtable(tbl, digits = digits, ...) |>
    print(
      include.colnames = include.colnames,
      include.rownames = include.rownames,
      hline.after = hline.after,
      comment = FALSE,
      tabular.environment = dplyr::if_else(longtable, "longtable", "tabular"),
      floating = FALSE,
      size = size,
      add.to.row = add.to.row,
      sanitize.text.function = function(x) {
        x
      }
    )
}
```

# Education and qualifications

```{r}
#| label: degrees
#| output: "asis"

tibble::tribble(
  ~Degree, ~Institution, ~Year ,
  "B.Sc. In Geographic Information Science", "Shaanxi Normal University",  "2025",
) |>
  baretable()
```

# Research Experience <!-- Employment history -->

```{r}
#| label: experience
#| output: "asis"

tibble::tribble(
  ~Duration, ~Position,
  "2026.6- ", "Research Assistant, The Hong Kong Polytechnic University", 
  "2025.9-2026.6", "Research Assistant, Eastern Institute of Technology, Ningbo",
  "2024.8-2025.8", "Research Intern, The Hong Kong University of Science and Technology (Guangzhou)", 
) |>
  baretable()
```

# Academic and research leadership

A grid table can hold a bullet list in a cell, so `why` carries several points
per entry. The `detailed` style sets those as a bulleted elaboration under the
entry. Here the headings already match, and no `fields` is needed.

::: {.entries style="detailed"}
+-------------+--------------------------+---------------------------------+
| when        | what                     | why                             |
+=============+==========================+=================================+
| 2019--2022  | Head                     | - Department of Econometrics &  |
|             |                          |   Business Statistics, Monash   |
|             |                          | - Led a department of over 70   |
|             |                          |   academic staff                |
+-------------+--------------------------+---------------------------------+
| 2001--2017  | Director                 | - Business & Economic           |
|             |                          |   Forecasting Unit, Monash      |
+-------------+--------------------------+---------------------------------+
:::

# Refereed research papers

```{r}
vitae::bibliography_entries("./lyu_publications.bib")
```

\vspace{0.1cm}

*Note: Publications under "Lyu, W." and "Lv, W." both refer to Wenbo Lyu.*

# Research interests

The `skills` style pairs a category with its members, written either as one
string in `with` or as a list in `why`.

::: {.entries style="skills"}
+---------------+----------------------------------------+
| what          | why                                    |
+===============+========================================+
| Methods       | - Forecast reconciliation              |
|               | - Functional time series               |
|               | - Anomaly detection                    |
|               | - Time series visualisation            |
+---------------+----------------------------------------+
| Applications  | - Electricity demand                   |
|               | - Demography                           |
|               | - Tourism                              |
+---------------+----------------------------------------+
| Software      | - R, Rcpp, Stan                        |
+---------------+----------------------------------------+
:::

# Grants

Where the data already lives in a data frame, the same options are given as
cell options instead, and the cell prints a table for the filter to pick up.
See the README for that form.

::: {.entries style="detailed"}
+-------------+----------------------------------------------+---------------------------------------+
| when        | what                                         | why                                   |
+=============+==============================================+=======================================+
| 2019--2024  | Australian Research Council Discovery Grant  | - *Forecasting large collections of   |
|             |                                              |   related time series*                |
|             |                                              | - \$540,000                           |
+-------------+----------------------------------------------+---------------------------------------+
| 2015--2018  | Australian Research Council Linkage Grant    | - *Forecasting electricity demand at  |
|             |                                              |   the household level*                |
|             |                                              | - \$320,000                           |
+-------------+----------------------------------------------+---------------------------------------+
:::
