---
name: Wenbo Lyu
position: "B.Sc. Graduate"
email: "lyu.geosocial@gmail.com"
scholar: NnaUl34AAAAJ
orcid: 0009-0002-6003-3800
#address: "Hong Kong"
#www: spatlyu.github.io
#phone: "+852 56212551"
linkedin: wenbo-lyu-824851403
github: SpatLyu
date: today
date-format: "MMMM YYYY"
headcolor: "000088"
format: 
    cv-pdf:
        show-doi: true
bibliography: lyu_publications.bib
---

\newcounter{bib}

```{r}
#| label: setup
#| include: false

knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  cache = FALSE
)

# Function to produce very basic table, no lines or headings
baretable = \(
  tbl,
  digits = 0,
  include.colnames = FALSE,
  include.rownames = FALSE,
  hline.after = NULL,
  size = getOption("xtable.size", NULL),
  add.to.row = getOption("xtable.add.to.row", NULL),
  longtable = FALSE,
  ...
) {
  xtable::xtable(tbl, digits = digits, ...) |>
    print(
      include.colnames = include.colnames,
      include.rownames = include.rownames,
      hline.after = hline.after,
      comment = FALSE,
      tabular.environment = dplyr::if_else(longtable, "longtable", "tabular"),
      floating = FALSE,
      size = size,
      add.to.row = add.to.row,
      sanitize.text.function = function(x) {
        x
      }
    )
}
```

# Education and qualifications

```{r}
#| label: degrees
#| output: "asis"

tibble::tribble(
    ~Degree, ~Institution, ~Year ,
    "B.Sc. In Geographic Information Science", "Shaanxi Normal University",  "2025",
) |>
    baretable()
```

# Research Experience <!-- Employment history -->

```{r}
#| label: experience
#| output: "asis"

tibble::tribble(
    ~Duration, ~Position,
    "2026.6- ", "Research Assistant, The Hong Kong Polytechnic University", 
    "2025.9-2026.6", "Research Assistant, Eastern Institute of Technology, Ningbo",
    "2024.8-2025.8", "Research Intern, The Hong Kong University of Science and Technology (Guangzhou)", 
) |>
    baretable()
```

# Research interests

- **Focus:** *Spatial causal inference* & high-performance computational tool development (*R packages*).
- **Methods:** *Empirical Dynamic Modeling (EDM)*, *information theory*, *ODEs*, and *counterfactual frameworks* for quantifying complex variable interactions.
- **Domains:** *Urban sustainability*, *climate change mitigation*, and global challenges.
- **Tech Stack:** *R, C++, Python* (Spatial analysis & open-source geospatial software).

# Selected research papers

```{r}
#| label: research-papers
#| output: asis

#papers = RefManageR::ReadBib("./lyu_publications.bib") 
papers = bibtex::read.bib('./lyu_publications.bib')
cat("\\begin{refsection}")
cat(paste0("\\nocite{", names(papers), "}"))
cat("\\printbibliography[heading=none]")
cat("\\end{refsection}")
```

\vspace{0.1cm}

*Note: Publications under "Lyu, W." and "Lv, W." both refer to Wenbo Lyu.*

# Unpublished working papers

```{r}
#| label: working-papers
#| output: asis

tibble::tribble(
    ~Title, ~Role, ~Status,
    "Quantifying pairwise directional influence between spatial variables: A reconstruction-based approach to asymmetric relationships", "Co-First Author (1st)", "Submitted to AAAG, currently under third-round review",
    "Spatial Pattern Entropy: A Symbolic Measure for Continuous Spatial Data", "Co-First Author (2nd)", "Submitted to IJGIS, currently under second-round review",
    "Spatially convergent partial cross mapping for identifying direct causal influence in cross-sectional data", "First Author", "Submitted to Comms Phys, currently in revision",
    "Unveiling interaction between spatial processes with information decomposition", "First Author", "In writing",
    "Pattern Causality for Detecting Interactions with the R Package pc", "First Author", "In writing",
    "coupling: Coupling Coordination Analysis in R", "First Author", "Plan",
    "Measuring spatial stratified heterogeneity via information imbalance", "First Author", "Plan",
    "Spatial causal discovery under latent confounders via deep orthogonal representation learning", "First Author", "Plan",
) |> 
    dplyr::select(Title) |> 
    baretable()
```

# Selected awards and honours

```{r}
#| label: awards
#| output: "asis"

tibble::tribble(
    ~Year, ~Award,
    "2024", "Longi Non-Education Major Scholarship", 
    "2024", "First Prize in the 13th National University Student GIS Application Skills Competition", 
    "2023", "Grand Prize in the 12th National University Student GIS Application Skills Competition", 
    "2023", "First Prize in the Second National University Student Ecological Environment Management Research Innovation Competition", 
    "2023", "Second Prize of the 5th 'Guodi Cup' National College Student Natural Resource Science and Technology Competition", 
    "2021", "Outstanding Individual in Military Training Publicity for College Students, Shaanxi Normal University", 
) |>
    baretable()
```

# Software (R packages)

```{r}
#| label: packages-table
#| output: "asis"

data.frame(
    Package = c(
        "\\href{https://cran.r-project.org/package=spEDM}{\\texttt{spEDM}}", 
        "\\href{https://cran.r-project.org/package=tEDM}{\\texttt{tEDM}}", 
        "\\href{https://cran.r-project.org/package=pc}{\\texttt{pc}}", 
        "\\href{https://cran.r-project.org/package=gdverse}{\\texttt{gdverse}}", 
        "\\href{https://cran.r-project.org/package=sdsfun}{\\texttt{sdsfun}}", 
        "\\href{https://cran.r-project.org/package=coupling}{\\texttt{coupling}}",
        "\\href{https://cran.r-project.org/package=infoxtr}{\\texttt{infoxtr}}"
    ),
    Description = c(
        "Spatial Empirical Dynamic Modeling",
        "Temporal Empirical Dynamic Modeling",
        "Pattern Causality Analysis",
        "Analysis of Spatial Stratified Heterogeneity",
        "Spatial Data Science Complementary Features",
        "Coupling Coordination Analysis",
        "Information-Theoretic Measures for Revealing Variable Interactions"
    )
) |>
    baretable()
```