---
name: Wenbo Lv
position: "undergraduate"
github: SpatLyu
www: spatlyu.github.io
orcid: 0009-0002-6003-3800
email: "lyu.geosocial@gmail.com"
address: "Xi'an, Shaanxi"
# date: "`r Sys.Date()`"
output: vitae::hyndman
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

# Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Geographic Information Science", "2021-2025", "Shaanxi Normal University", "Xi'an, Shaanxi",
) %>%
  detailed_entries(Degree, Year, Institution, Where)
```

# Some stuff about me

- I am passionate about **developing innovative spatial analysis methods** that **leverage spatial relationships**, such as *spatial dependence*, *spatial heterogeneity*, and *geographical similarity*, to advance *urban sustainability* and *climate change mitigation* efforts.
- I am proficient in *data analysis*, *statistical modeling*, and developing *R packages*, as well as open-source analytical software using **R**, **C++**, and **Python**.
- I have experience implementing complex statistical algorithms in **C++** and can efficiently integrate **torch** for machine learning applications.

# Publications

```{r}
bibliography_entries("lyu_publications.bib")
```

# Honor

```{r}
tribble(
  ~ Awards, ~ Date,
  "Grand Prize in the 12th National University Student GIS Application Skills Competition", "2023.12",
  "First Prize in the Second National University Student Ecological Environment Management Research Innovation Competition", "2023.11",
  "Second Prize of the 5th 'Guodi Cup' National College Student Natural Resource Science and Technology Competition, China Society of Natural Resources", "2023.12",
  "Outstanding Individual in Military Training Publicity for College Students, Shaanxi Normal University", "2021.10",
  "National University Student Innovation and Entrepreneurship Training Program Qualified Completion", "2024.06"
) %>%
  detailed_entries(Awards,Date)
```

# Unpublished

```{r}
tribble(
  ~ Name, ~ Role, ~ Status,
  "gdverse: An R package facilitating spatial stratified heterogeneity analysis with geographical detector models", "First Author", "Submitting to TGIS",
  'On the role of "spatial" in spatial stratified heterogeneity', "First Author", "In writing",
  "On the direction of spatial associations under spatial stratified heterogeneity", "First Author", "In writing",
  "Geocomplexity Mitigates Spatial Bias", "First Author", "In writing"
) %>%
  detailed_entries(Name, Role, Status)
```

# In research

```{r}
tribble(
  ~ Name, ~ Role, ~ Date, ~ Details,
  "Extract Urban Spatial Boundaries in Xi'an City Using Deep Learning", "Leader", "",
  "Utilized advanced spatial sampling methods and unsupervised algorithms to automatically generate sample sets. Employed geographically weighted neural networks combined with logistic regression to extract urban spatial boundaries"
) %>%
  detailed_entries(Name, Role, ,Date ,Details)
```

# Developed Spatial Analysis Toolkit

| Package        | Description                                                   | Source Code                                | Language       |
|-----------------|---------------------------------------------------------|------------------------------------------------------|---------------------|
| gdverse       | Analysis of Spatial Stratified Heterogeneity                  | <https://github.com/stscl/gdverse>         | R, C++, Python |
| geocomplexity | Mitigate Spatial Bias Through Geographical Complexity         | <https://github.com/ausgis/geocomplexity>  | C++, R, C |
| sesp          | Spatially Explicit Stratified Power                           | <https://github.com/ausgis/sesp>           | R, C++         |
| sdsfun        | Spatial Data Science Complementary Features                   | <https://github.com/stscl/sdsfun>          | R, C++         |
| geosimilarity | Geographically Optimal Similarity                             | <https://github.com/ausgis/geosimilarity>  | R              |
| GD            | Geographical Detectors for Assessing Spatial Factors          | <https://github.com/ausgis/GD>             | R              |
| geocn         | Loads Spatial Data Sets of China                              | <https://github.com/stscl/geocn>           | R              |
| qgisprocess   | R package to use QGIS processing algorithms                   | <https://github.com/r-spatial/qgisprocess> | R              |
| spEcula       | Spatial Prediction Methods In R                               | <https://github.com/SpatLyu/spEcula>       | R              |
| tidyrgeoda    | A tidy interface for rgeoda                                   | <https://github.com/SpatLyu/tidyrgeoda>    | R              |
<!-- | Rsagacmd      | A package for linking R with the open-source SAGA-GIS         | <https://github.com/stevenpawley/Rsagacmd> | R              | -->
<!-- | SpatBox       | A Python Library For GeoSpatial Data Propressing and Modeling | <https://github.com/SpatLyu/spatbox>     | Python         | -->