---
name: Wenbo Lv
position: "undergraduate"
pronouns: he/him
www: spatlyu.github.io
email: "lyu.geosocial@gmail.com"
github: SpatLyu
orcid: 0009-0002-6003-3800
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::moderncv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

# Some stuff about me

 * I am deeply interested in developing spatial analysis methods based on spatial relationships (such as spatial dependence, spatial heterogeneity, geographical similarity).
 * I am proficient in R language data analysis, statistical modeling, and R package development.
 * I am familiar with implementing computationally complex statistical algorithms using C++, and I can flexibly call upon torch.

# Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Geographic Information Science", "2021-2025", "Shaanxi Normal University", "Xi'an, Shaanxi",
) %>%
  detailed_entries(Degree, Year, Institution, Where)
```



# Publications

```{r}
library(dplyr)
knitr::write_bib(c("vitae", "tibble"), "packages.bib")

bibliography_entries("packages.bib") %>%
  arrange(desc(author$family), issued)
```

