---
name: Wenbo Lv
position: "B.Sc. Graduate"
github: SpatLyu
www: spatlyu.github.io
orcid: 0009-0002-6003-3800
email: "lyu.geosocial@gmail.com"
address: "Ningbo"
# date: "`r Sys.Date()`"
output: vitae::hyndman
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

# Some stuff about me

-   My research interests lie in **advancing methodologies in spatial causal inference** and **developing high-performance computational tools**, with a primary focus on *R packages*.
-   I specialize in *data analysis*, *statistical modeling*, and developing open-source analytical tools, including *R packages*, using **R**, **C++**, and **Python**, with a strong focus on *spatial analysis*. I actively contribute to the R geospatial community and am dedicated to advancing open-source geospatial software.
-   Currently, my work centers on **Empirical Dynamic Modeling (EDM)** framework for modeling *dynamic system*, **information theory** for quantifying *information flow* and *causal interdependence*, **ordinary differential equations (ODEs)** for characterizing *spatiotemporal processes* and *system evolution*, as well as **counterfactual** and **potential outcomes** framework for estimating *causal effects*. I am particularly interested in leveraging these approaches to address critical challenges in *urban sustainability*, *climate change mitigation*, and broader global issues.

# Education

```{r}
tibble::tribble(
  ~ Degree, ~ Duration, ~ Institution, ~ Where,
  "B.Sc. In Geographic Information Science", "2021.8-2025.6", "Shaanxi Normal University", "Xi'an, Shaanxi",
) %>%
  detailed_entries(Degree, Duration, Institution, Where)
```

# Research Experience

```{r}
tibble::tribble(
  ~ Position, ~ Duration, ~ Institution, ~ Where,
  "Research Assistant", "2025.9-2026.9", "EITech", "Ningbo, Zhejiang",
  "Research Assistant", "2025.2-2025.8", "PolyU-SZRI", "Shenzhen, Guangdong",
  "Visiting Student", "2024.8-2025.6", "HKUST(GZ)", "Guangzhou, Guangdong",
) %>%
  detailed_entries(Position, Duration, Institution, Where)
```

# Publications

```{r}
bibliography_entries("../lyu_publications.bib")
```

# Honor

```{r}
tibble::tribble(
  ~ Awards, ~ Date,
  "Longi Non-Education Major Scholarship", "2024.12",
  "First Prize in the 13th National University Student GIS Application Skills Competition", "2024.11",
  "National University Student Innovation and Entrepreneurship Training Program Qualified Completion", "2024.06",
  "Grand Prize in the 12th National University Student GIS Application Skills Competition", "2023.12",
  "First Prize in the Second National University Student Ecological Environment Management Research Innovation Competition", "2023.11",
  "Second Prize of the 5th 'Guodi Cup' National College Student Natural Resource Science and Technology Competition, China Society of Natural Resources", "2023.12",
  "Outstanding Individual in Military Training Publicity for College Students, Shaanxi Normal University", "2021.10",
) %>%
  detailed_entries(Awards,Date)
```

# Unpublished

```{r}
tibble::tribble(
  ~ Name, ~ Role, ~ Status,
  "Measuring causal strengths by geographical cross mapping cardinality",      
  "First Author", "Submitted to IJGIS, currently under decision",
  "Causal discovery in urban data with temporal empirical dynamic modeling: The R package tEDM",
  "First Author", "Submitted to CEUS, currently in revision",
  # "Spatially convergent partial cross mapping for identifying direct causal influence in cross-sectional data",
  # "First Author", "In writting",
  "Convergence-Diagnostic Geographical Pattern Causality for Robust Spatial Causal Discovery",
  "First Author", "In writting",
  "Quantifying Information Flows in Spatial Processes",
  "First Author", "Plan",
  "gobi: General ODE-Based Causal Inference in R",
  "First Author", "Plan",
  # "Agricultural policies reshape cropland patterns with varying impacts - a case of soybeans from Heilongjiang Province", "Third Author", "Submitted to Land Use Policy, currently under review",
  # "Geocomplexity-heterogeneity model for identifying spatial pattern drivers",
  # "Co-Author", "Submitted to IJGIS, currently under review",
    # "New-type Urbanization Policy,Urban Expansion,and Employment Quality in Chinese Cities: Evidence from a Quasi-natural Experiment in China",
  # "Co-Author", "Submitted to JGSA, currently with editor",
  # "Township-scale vegetation greening in the Guangdong-Hong Kong-Macao Greater Bay Area: Pathways, spatiotemporal heterogeneity, causality, and driving mechanisms",
  # "Co-Author", "Submitted to GRS, currently under review"
) %>%
  detailed_entries(Name, Role, Status)
```

<!-- # In research -->

<!-- ```{r} -->

<!-- tribble( -->

<!--   ~ Name, ~ Role, ~ Date, ~ Details, -->

<!--   "Extract Urban Spatial Boundaries in Xi'an City Using Deep Learning", "Leader", "", -->

<!--   "Utilized advanced spatial sampling methods and unsupervised algorithms to automatically generate sample sets. Employed geographically weighted neural networks combined with logistic regression to extract urban spatial boundaries" -->

<!-- ) %>% -->

<!--   detailed_entries(Name, Role, Date, Details) -->

<!-- ``` -->

# Developed Spatial Analysis Toolkit

| Package | Description | Language |
|----|----|----|
| [spEDM](https://cran.r-project.org/package=spEDM) | Spatial Empirical Dynamic Modeling | C++, R |
| [tEDM](https://cran.r-project.org/package=tEDM) | Temporal Empirical Dynamic Modeling | C++, R |
| [gobi](https://github.com/stscl/gobi) | General ODE-Based Causal Inference | C++, R |
| [infocausality](https://github.com/stscl/infocausality) | Information-Theoretic Measure of Causality | C++, Python, R |
| [gdverse](https://cran.r-project.org/package=gdverse) | Analysis of Spatial Stratified Heterogeneity | R, C++, Python |
| [sdsfun](https://cran.r-project.org/package=sdsfun) | Spatial Data Science Complementary Features | R, C++ |
| [geocomplexity](https://cran.r-project.org/package=geocomplexity) | Mitigate Spatial Bias Through Geographical Complexity | C++, R, C |
| [HSAR](https://cran.r-project.org/package=HSAR) | Hierarchical Spatial Autoregressive Model | C++, R |
| [GD](https://cran.r-project.org/package=GD) | Geographical Detectors for Assessing Spatial Factors | R |
| [geosimilarity](https://cran.r-project.org/package=) | Geographically Optimal Similarity | R |

<!-- | [itmsa](https://cran.r-project.org/package=itmsa) | Information-Theoretic Measures for Spatial Association | C++, R | -->

<!-- | [sesp](https://github.com/stscl/sesp) | Spatially Explicit Stratified Power | R, C++ | -->

<!-- | [cisp](https://cran.r-project.org/package=cisp) | A Correlation Indicator Based On Spatial Patterns | R | -->

<!-- | [geocn](https://github.com/stscl/geocn) | Loads Spatial Data Sets of China | R | -->

<!-- | [spEcula](https://github.com/SpatLyu/spEcula) | Spatial Prediction Methods In R | R | -->

<!-- | [tidyrgeoda](https://github.com/SpatLyu/tidyrgeoda) | A tidy interface for rgeoda | R | -->

<!-- | [figpatch](https://cran.r-project.org/package=figpatch) | Easily Arrange External Figures with Patchwork Alongside 'ggplot2' Figures | R | -->

<!-- | [qgisprocess](https://cran.r-project.org/package=qgisprocess) | R package to use QGIS processing algorithms | R | -->

<!-- | [Rsagacmd](https://cran.r-project.org/package=Rsagacmd) | A package for linking R with the open-source SAGA-GIS | R | -->

<!-- | [SpatBox](https://github.com/SpatLyu/spatbox) | A Python Library For GeoSpatial Data Propressing and Modeling | Python | -->
