---
name: Wenbo Lv
position: "B.Sc. Graduate"
github: SpatLyu
www: spatlyu.github.io
orcid: 0009-0002-6003-3800
email: "lyu.geosocial@gmail.com"
address: "Ningbo"
# date: "`r Sys.Date()`"
output: vitae::hyndman
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

# Some stuff about me

- My research interests lie in **advancing methodologies in spatial causal inference** and **developing high-performance computational tools**, with a primary focus on *R packages*.
- Currently, my work centers on **Empirical Dynamic Modeling (EDM)** framework for modeling *dynamic system* and **Difference-in-Differences (DID)** methods for *event studies*. I am particularly interested in leveraging these approaches to address critical challenges in *urban sustainability*, *climate change mitigation*, and broader global issues.
- I specialize in *data analysis*, *statistical modeling*, and developing open-source analytical tools, including *R packages*, using **R**, **C++**, and **Python**, with a strong focus on *spatial analysis*. I actively contribute to the R geospatial community and am dedicated to advancing open-source geospatial software.

# Education

```{r}
tibble::tribble(
  ~ Degree, ~ Duration, ~ Institution, ~ Where,
  "B.Sc. In Geographic Information Science", "2021.8-2025.6", "Shaanxi Normal University", "Xi'an, Shaanxi",
) %>%
  detailed_entries(Degree, Duration, Institution, Where)
```

# Research Experience

```{r}
tibble::tribble(
  ~ Position, ~ Duration, ~ Institution, ~ Where,
  "Research Assistant", "2025.9-2026.9", "EITech", "Ningbo, Zhejiang",
  "Research Assistant", "2025.2-2025.8", "PolyU", "Shenzhen, Guangdong",
  "Visiting Student", "2024.8-2025.6", "HKUST(GZ)", "Guangzhou, Guangdong",
) %>%
  detailed_entries(Position, Duration, Institution, Where)
```

# Publications

```{r}
bibliography_entries("../lyu_publications.bib")
```

# Honor

```{r}
tibble::tribble(
  ~ Awards, ~ Date,
  "Longi Non-Education Major Scholarship", "2024.12",
  "First Prize in the 13th National University Student GIS Application Skills Competition", "2024.11",
  "National University Student Innovation and Entrepreneurship Training Program Qualified Completion", "2024.06",
  "Grand Prize in the 12th National University Student GIS Application Skills Competition", "2023.12",
  "First Prize in the Second National University Student Ecological Environment Management Research Innovation Competition", "2023.11",
  "Second Prize of the 5th 'Guodi Cup' National College Student Natural Resource Science and Technology Competition, China Society of Natural Resources", "2023.12",
  "Outstanding Individual in Military Training Publicity for College Students, Shaanxi Normal University", "2021.10",
) %>%
  detailed_entries(Awards,Date)
```

# Unpublished

```{r}
tibble::tribble(
  ~ Name, ~ Role, ~ Status,
  "Measuring causal strengths by geographical cross mapping cardinality", "First Author", "Submitted to IJGIS, currently second-round revision",
  "Causal discovery in urban data with temporal empirical dynamic modeling: The R package tEDM",
  "First Author", "Submitted to CEUS, currently with editor",
  # "Zoning-dependent determinants of greenspace exposure: Evidence from multi-source remote sensing observations in China","Second Author", "Submitted to IEEE Geoscience and Remote Sensing Letter, currently under review",
  "Agricultural policies reshape cropland patterns with varying impacts - a case of soybeans from Heilongjiang Province", "Third Author", "Submitted to Land Use Policy, currently under review",
  # "Spatially convergent partial cross mapping for identifying direct causal influence in cross-sectional data",
  # "First Author", "In writting",
  "Decomposing spatial causality through mutual information", 
  "First Author", "Plan",
  # "On the role of explicit spatial information in stratified heterogeneity", "First Author", "Plan",
  # "Geocomplexity Mitigates Spatial Bias", "First Author", "Plan"
) %>%
  detailed_entries(Name, Role, Status)
```

<!-- # In research -->

<!-- ```{r} -->
<!-- tribble( -->
<!--   ~ Name, ~ Role, ~ Date, ~ Details, -->
<!--   "Extract Urban Spatial Boundaries in Xi'an City Using Deep Learning", "Leader", "", -->
<!--   "Utilized advanced spatial sampling methods and unsupervised algorithms to automatically generate sample sets. Employed geographically weighted neural networks combined with logistic regression to extract urban spatial boundaries" -->
<!-- ) %>% -->
<!--   detailed_entries(Name, Role, Date, Details) -->
<!-- ``` -->

# Developed Spatial Analysis Toolkit

| Package        | Description                                                   | Source Code                                | Language       |
|-------------------|-----------------------------------------------------------|------------------------------------------------------------|--------------------|
| spEDM         | Spatial Empirical Dynamic Modeling                            | <https://github.com/stscl/spEDM>          | C++, R         |
| tEDM          | Temporal Empirical Dynamic Modeling                           | <https://github.com/stscl/tEDM>           | C++, R         |
| gdverse       | Analysis of Spatial Stratified Heterogeneity                  | <https://github.com/stscl/gdverse>        | R, C++, Python |
| itmsa         | Information-Theoretic Measures for Spatial Association        |  <https://github.com/stscl/itmsa>         | C++, R         |
| sdsfun        | Spatial Data Science Complementary Features                   | <https://github.com/stscl/sdsfun>         | R, C++         |
| geocomplexity | Mitigate Spatial Bias Through Geographical Complexity         | <https://github.com/ausgis/geocomplexity> | C++, R, C      |
| HSAR          | Hierarchical Spatial Autoregressive Model                     | <https://github.com/spatlyu/hsar>         | C++, R         |
| GD            | Geographical Detectors for Assessing Spatial Factors          | <https://github.com/ausgis/GD>             | R              |
| sesp          | Spatially Explicit Stratified Power                           | <https://github.com/stscl/sesp>           | R, C++         |
| cisp          | A Correlation Indicator Based On Spatial Patterns             | <https://github.com/stscl/cisp>           | R              |
| geosimilarity | Geographically Optimal Similarity                             | <https://github.com/ausgis/geosimilarity>  | R              |
| geocn         | Loads Spatial Data Sets of China                              | <https://github.com/stscl/geocn>          | R              |
| figpatch      | Easily Arrange External Figures with Patchwork Alongside 'ggplot2' Figures | <https://github.com/spatlyu/figpatch>          | R              |
| qgisprocess   | R package to use QGIS processing algorithms                   | <https://github.com/r-spatial/qgisprocess> | R              |
| spEcula       | Spatial Prediction Methods In R                               | <https://github.com/SpatLyu/spEcula>       | R              |
| tidyrgeoda    | A tidy interface for rgeoda                                   | <https://github.com/SpatLyu/tidyrgeoda>    | R              |
<!-- | Rsagacmd      | A package for linking R with the open-source SAGA-GIS         | <https://github.com/stevenpawley/Rsagacmd> | R              | -->
<!-- | SpatBox       | A Python Library For GeoSpatial Data Propressing and Modeling | <https://github.com/SpatLyu/spatbox>     | Python         | -->