---
name: Wenbo Lv
position: "undergraduate"
github: SpatLyu
www: spatlyu.github.io
orcid: 0009-0002-6003-3800
email: "lyu.geosocial@gmail.com"
address: "Xi'an, Shaanxi"
# date: "`r Sys.Date()`"
output: vitae::hyndman
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

# Some stuff about me

- My research interests lie in **advancing methodologies in spatial causal inference** and **developing high-performance computational tools**, with a primary focus on *R packages*.
- Currently, my work centers on **Empirical Dynamic Modeling (EDM)** framework for modeling *dynamic system* and **Difference-in-Differences (DID)** methods for *event studies*. I am particularly interested in leveraging these approaches to address critical challenges in *urban sustainability*, *climate change mitigation*, and broader global issues.
- I possess expertise in *data analysis*, *statistical modeling*, and the development of *R packages* and open-source analytical tools utilizing **R**, **C++**, and **Python**.
- I have contributed to the **development** and **maintenance** of several open-source spatial analysis tools within the R community and remain dedicated to **advancing open-source geospatial analysis software**.

# Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "BSc In Geographic Information Science", "2021-2025", "Shaanxi Normal University", "Xi'an, Shaanxi",
) %>%
  detailed_entries(Degree, Year, Institution, Where)
```

# Publications

```{r}
bibliography_entries("../lyu_publications.bib")
```

# Honor

```{r}
tribble(
  ~ Awards, ~ Date,
  "Longi Non-Education Major Scholarship", "2024.12",
  "First Prize in the 13th National University Student GIS Application Skills Competition", "2024.11",
  "National University Student Innovation and Entrepreneurship Training Program Qualified Completion", "2024.06",
  "Grand Prize in the 12th National University Student GIS Application Skills Competition", "2023.12",
  "First Prize in the Second National University Student Ecological Environment Management Research Innovation Competition", "2023.11",
  "Second Prize of the 5th 'Guodi Cup' National College Student Natural Resource Science and Technology Competition, China Society of Natural Resources", "2023.12",
  "Outstanding Individual in Military Training Publicity for College Students, Shaanxi Normal University", "2021.10"
) %>%
  detailed_entries(Awards,Date)
```

# Unpublished

```{r}
tribble(
  ~ Name, ~ Role, ~ Status,
  "Measuring causal associations by geographical cross mapping cardinality", "First Author", "Submitted to IJGIS",
  # "Zoning-dependent determinants of greenspace exposure: Evidence from multi-source remote sensing observations in China","Second Author", "Submitted to IEEE Geoscience and Remote Sensing Letter, currently under review",
  "Agricultural policies reshape cropland patterns with varying impacts - a case of soybeans from Heilongjiang Province", "Third Author", "Submitted to Land Use Policy, currently under review",
  "Decomposing spatial causality through mutual information", 
  "First Author", "Plan",
  "On the role of explicit spatial information in stratified heterogeneity", "First Author", "Plan",
  "Geocomplexity Mitigates Spatial Bias", "First Author", "Plan"
) %>%
  detailed_entries(Name, Role, Status)
```

<!-- # In research -->

<!-- ```{r} -->
<!-- tribble( -->
<!--   ~ Name, ~ Role, ~ Date, ~ Details, -->
<!--   "Extract Urban Spatial Boundaries in Xi'an City Using Deep Learning", "Leader", "", -->
<!--   "Utilized advanced spatial sampling methods and unsupervised algorithms to automatically generate sample sets. Employed geographically weighted neural networks combined with logistic regression to extract urban spatial boundaries" -->
<!-- ) %>% -->
<!--   detailed_entries(Name, Role, Date, Details) -->
<!-- ``` -->

# Developed Spatial Analysis Toolkit

| Package        | Description                                                   | Source Code                                | Language       |
|-------------------|-----------------------------------------------------------|------------------------------------------------------------|--------------------|
| spEDM         | Spatial Empirical Dynamic Modeling                            | <https://github.com/stscl/spEDM>           | C++, R         |
| gdverse       | Analysis of Spatial Stratified Heterogeneity                  | <https://github.com/stscl/gdverse>         | R, C++, Python |
| itmsa   | Information-Theoretic Measures for Spatial Association  |              <https://github.com/stscl/itmsa>          | C++, R         |
| GD            | Geographical Detectors for Assessing Spatial Factors          | <https://github.com/ausgis/GD>             | R              |
| sdsfun        | Spatial Data Science Complementary Features                   | <https://github.com/stscl/sdsfun>          | R, C++         |
| sesp          | Spatially Explicit Stratified Power                           | <https://github.com/stscl/sesp>            | R, C++         |
| cisp          | A Correlation Indicator Based On Spatial Patterns             | <https://github.com/stscl/cisp>            | R              |
| geocomplexity | Mitigate Spatial Bias Through Geographical Complexity         | <https://github.com/ausgis/geocomplexity>  | C++, R, C      |
| geosimilarity | Geographically Optimal Similarity                             | <https://github.com/ausgis/geosimilarity>  | R              |
| geocn         | Loads Spatial Data Sets of China                              | <https://github.com/stscl/geocn>           | R              |
| qgisprocess   | R package to use QGIS processing algorithms                   | <https://github.com/r-spatial/qgisprocess> | R              |
| spEcula       | Spatial Prediction Methods In R                               | <https://github.com/SpatLyu/spEcula>       | R              |
| tidyrgeoda    | A tidy interface for rgeoda                                   | <https://github.com/SpatLyu/tidyrgeoda>    | R              |
<!-- | Rsagacmd      | A package for linking R with the open-source SAGA-GIS         | <https://github.com/stevenpawley/Rsagacmd> | R              | -->
<!-- | SpatBox       | A Python Library For GeoSpatial Data Propressing and Modeling | <https://github.com/SpatLyu/spatbox>     | Python         | -->