---
name: Wenbo Lv
position: "undergraduate"
github: SpatLyu
www: spatlyu.github.io
orcid: 0009-0002-6003-3800
email: "lyu.geosocial@gmail.com"
address: "Xi'an, Shaanxi"
# date: "`r Sys.Date()`"
output: vitae::hyndman
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

# Some stuff about me

- I am passionate about **developing innovative spatial analysis methods** that leverage **spatial relationships**, such as *spatial dependence*, *spatial heterogeneity*, and *geographical similarity*, to advance *urban sustainability* and *climate change mitigation* efforts.
- I possess expertise in *data analysis*, *statistical modeling*, and the development of *R packages* and open-source analytical tools utilizing **R**, **C++**, and **Python**.
- I have contributed to the **development** and **maintenance** of several open-source spatial analysis tools within the R community and remain dedicated to **advancing open-source geospatial analysis software**.

# Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "BSc In Geographic Information Science", "2021-2025", "Shaanxi Normal University", "Xi'an, Shaanxi",
) %>%
  detailed_entries(Degree, Year, Institution, Where)
```

# Publications

```{r}
bibliography_entries("../lyu_publications.bib")
```

# Honor

```{r}
tribble(
  ~ Awards, ~ Date,
  "Grand Prize in the 12th National University Student GIS Application Skills Competition", "2023.12",
  "First Prize in the Second National University Student Ecological Environment Management Research Innovation Competition", "2023.11",
  "Second Prize of the 5th 'Guodi Cup' National College Student Natural Resource Science and Technology Competition, China Society of Natural Resources", "2023.12",
  "Outstanding Individual in Military Training Publicity for College Students, Shaanxi Normal University", "2021.10",
  "National University Student Innovation and Entrepreneurship Training Program Qualified Completion", "2024.06"
) %>%
  detailed_entries(Awards,Date)
```

# Unpublished

```{r}
tribble(
  ~ Name, ~ Role, ~ Status,
  "gdverse: An R package for spatial stratified heterogeneity family", "First Author", "Submitting to TGIS",
  "On the role of explicit spatial information in stratified heterogeneity", "First Author", "In writing",
  "A correlation indicator based on spatial patterns", "First Author", "In writing",
  "Geocomplexity Mitigates Spatial Bias", "First Author", "In writing"
) %>%
  detailed_entries(Name, Role, Status)
```

# In research

```{r}
tribble(
  ~ Name, ~ Role, ~ Date, ~ Details,
  "Extract Urban Spatial Boundaries in Xi'an City Using Deep Learning", "Leader", "",
  "Utilized advanced spatial sampling methods and unsupervised algorithms to automatically generate sample sets. Employed geographically weighted neural networks combined with logistic regression to extract urban spatial boundaries"
) %>%
  detailed_entries(Name, Role, Date, Details)
```

# Developed Spatial Analysis Toolkit

| Package        | Description                                                   | Source Code                                | Language       |
|-----------------|---------------------------------------------------------|------------------------------------------------------|---------------------|
| gdverse       | Analysis of Spatial Stratified Heterogeneity                  | <https://github.com/stscl/gdverse>         | R, C++, Python |
| sesp          | Spatially Explicit Stratified Power                           | <https://github.com/stscl/sesp>            | R, C++         |
| geocomplexity | Mitigate Spatial Bias Through Geographical Complexity         | <https://github.com/ausgis/geocomplexity>  | C++, R, C |
| cisp          | A Correlation Indicator Based On Spatial Patterns             | <https://github.com/stscl/cisp>            | R              |
| geosimilarity | Geographically Optimal Similarity                             | <https://github.com/ausgis/geosimilarity>  | R              |
| GD            | Geographical Detectors for Assessing Spatial Factors          | <https://github.com/ausgis/GD>             | R              |
| sdsfun        | Spatial Data Science Complementary Features                   | <https://github.com/stscl/sdsfun>          | R, C++         |
| geocn         | Loads Spatial Data Sets of China                              | <https://github.com/stscl/geocn>           | R              |
| qgisprocess   | R package to use QGIS processing algorithms                   | <https://github.com/r-spatial/qgisprocess> | R              |
| spEcula       | Spatial Prediction Methods In R                               | <https://github.com/SpatLyu/spEcula>       | R              |
| tidyrgeoda    | A tidy interface for rgeoda                                   | <https://github.com/SpatLyu/tidyrgeoda>    | R              |
<!-- | Rsagacmd      | A package for linking R with the open-source SAGA-GIS         | <https://github.com/stevenpawley/Rsagacmd> | R              | -->
<!-- | SpatBox       | A Python Library For GeoSpatial Data Propressing and Modeling | <https://github.com/SpatLyu/spatbox>     | Python         | -->